Results

### 2018-07-15 02_analysis.Rmd
Add session info
Add caption labels

```{r tbl-single-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_i,
          diffs_coef_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-single-diffs.md"))
```

@@

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-diffs.md"))
```

@@

```{r tbl-single-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_i,
          diffs_coef_likely_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-single-diffs.md"))
```

@@

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-diffs.md"))
```

>>>>

```{r tbl-single-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_i,
          diffs_coef_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:amount-single-diffs}") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-single-diffs.md"))
```

@@

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions {#tbl:amount-diffs}') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-diffs.md"))
```

@@

```{r tbl-single-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_i,
          diffs_coef_likely_pairs_detail_f) %>% 
  select(`Frame` = pair, `∆~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = "Median difference between likelihood to donate across single conditions {#tbl:likelihood-single-diffs}") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-single-diffs.md"))
```

@@

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown~median~` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions {#tbl:likelihood-diffs}') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-diffs.md"))
```

# Session info

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info}
sessionInfo()
```

</div>
